Subj_Arousal_bayes_prevalence

### 2022-05-25 Paper_Analyses_subj_obje_arousal.Rmd
change of storage location

View(var.data)
# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)
InPosition::epCA.inference.battery()

@@

>>>>

View(var.data)
# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

clustering_new_pre_PCA3.1

colnames(clustering_new_pre_PCA3.1)

library(prettyGraphs)

min(clustering_new_pre_PCA3.1$log_BIO_CDA.PhasicMax, na.rm = TRUE)
testjustpca <-InPosition::epPCA.inference.battery(clustering_new_pre_PCA3.1[,5:7], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

?InPosition::epPCA.inference.battery

clustering_new_pre_PCA3.1$pc1<- testjustpca$Fixed.Data$ExPosition.Data$fi[,1]
clustering_new_pre_PCA3.1$pc2<- testjustpca$Fixed.Data$ExPosition.Data$fi[,2]
testjustpca$Fixed.Data$ExPosition.Data$fi

summary(lmer(arousal ~ (pc1 + pc2) + (1|ssid) + (1|stimDescription),
     data = clustering_new_pre_PCA3.1))

write_csv(clustering_new_pre_PCA3.1, "clustering_new_pre_PCA3.1new.csv")

InPosition::epCA.inference.battery()

@@

# 
colnames(clustering_new_pre_PCA_2_agg_by_val_sel)

min(clustering_new_pre_PCA_2_agg_by_val_sel$log_BIO_CDA.PhasicMax)
testjustpca2 <-InPosition::epPCA.inference.battery(clustering_new_pre_PCA_2_agg_by_val_sel[,3:5], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

clustering_new_pre_PCA_2_agg_by_val_sel$pc1 <- testjustpca2$Fixed.Data$ExPosition.Data$fi[,1]
clustering_new_pre_PCA_2_agg_by_val_sel$pc2 <- testjustpca2$Fixed.Data$ExPosition.Data$fi[,2]

summary(lmer(arousal ~ (pc1 + pc2) + (1|ssid),
     data = clustering_new_pre_PCA_2_agg_by_val_sel))

### 2022-05-25 Subj_Obj_Ar_Bayes_Prev.Rmd
change of storage location

  colnames(p)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(p)

@@

@@

valence
```{r}

@@

scales::rescale(0)
db_full4new_stim_screen_pupil_nopract_no_outl%>%
  group_by(ssid)%>%
  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(rescaled_y = scales::rescale_max(testdensity_y, to = c(0,.4)))%>%
  ggplot(aes(x = pup_basCor))+
  stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
  # geom_density()+
  geom_jitter(aes( x = pup_basCor_mean, y = rescaled_y),
              width = .1, height = 0)
  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))
  geom_jitter()
  stat_summary(geom = "pointrange")

testdensity$data.name

 c(density(db_full4new_stim_screen_pupil_nopract_no_outl$ssid,n=n)$x, density(bar,n=n)$x)

@@

```{r cars}
summary(cars)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

  colnames(p)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(p)
```

@@

Now Level 2 test

@@

@@

scales::rescale(0)

bind_bayes1 <- left_join(as.data.frame(p), as.data.frame(estimate), by = "sid")
bind_bayes2 <- left_join(as.data.frame(bind_bayes1), as.data.frame(se), by = "sid")
bind_bayes2

bind_test<- bind_cols(p, estimate, se)

db_full4new_stim_screen_pupil_nopract_no_outl%>%
  group_by(ssid)%>%
  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(rescaled_y = scales::rescale_max(testdensity_y, to = c(0,.4)))%>%
  ggplot(aes(x = pup_basCor))+
  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
  geom_jitter(aes( x = pup_basCor_mean, y = rescaled_y),
              width = .1, height = 0)

bind_bayes2$xdensity<- testdensity[["x"]]
bind_bayes2$ydensity<- testdensity[["y"]]

testgensity

bind_bayes2 %>%

  group_by(sid)%>%
  # mutate(testdensity_x = density(arousal_c.x, n = 2)$x,
  #        testdensity_y = density(arousal_c.x, n = 2)$y)%>%

  ggplot(aes(x = arousal_c.x))+
   # stat_function(fun=dgamma, args=list(shape=1))
  geom_density() +
  geom_point(aes(x = xdensity, y =ydensity))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), arousal_c.y, color = arousal_c.x<.05))+
  geom_point()+
  geom_pointrange(aes(ymin = arousal_c.y- arousal_c, ymax = arousal_c.y+ arousal_c ))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), valence_c.y, color = valence_c.x<.05))+
  geom_point()+
  geom_pointrange(aes(ymin = valence_c.y- valence_c, ymax = valence_c.y+ valence_c ))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), `valence:arousal.y` , 
             color = `valence:arousal.x` <.05))+
  geom_point()+
  geom_pointrange(aes(ymin = `valence:arousal.y` - `valence:arousal`, 
                      ymax = `valence:arousal.y` + `valence:arousal` ))

@@

Try with the timecourse now.
start with only one predictor - arousal

then plot the effect size in terms of a heatmap

tmp.df4_full_stim_downs_jun2021_60bins_NT<- subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    Group == "NT")

b = 1

subject_id2<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT$ssid)
s = 1

b = 1

testtimecourseforbayprev<-   subset(tmp.df4_full_stim_downs_jun2021_60bins_NT,
                                    ssid =  subject_id[s],
                                    timebin_no == nbins[b])

unique(testtimecourseforbayprev$timebin_no)

tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  group_by(ssid, timebin_no)%>%
  summarise_at(c("pup_basCor"), mean, na.rm = TRUE)

# try and figure out how many timebins per participant we need to cerate to hold data
tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  subset(timebin_no<56)%>%
  group_by(ssid, timebin_no)%>%
  summarise_at(c("pup_basCor"), mean, na.rm = TRUE) %>%
    group_by(ssid)%>%
  mutate(n_timebin = n())
  # total of 3025 rows
  #  summarise_at(c("pup_basCor", "n_timebin"), mean, na.rm = TRUE)

tmp.df4_full_stim_downs_jun2021_60bins_NT_55<- tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  subset(timebin_no<56)

# create the dataset to hold participant, timebin code, statistics for each timebin
# seems like the majority have 55

nsubj_2 = 55
n_bins_2 = 55

timecourse_60bin_result_df_for_bp <-timecourse_60bin_result_df <- data.frame(
  ssid = rep(NA, nsubj_2*n_bins_2),
  timebins= rep(NA, nsubj_2*n_bins_2), 
                                       Estimate_ar= rep(NA, nsubj_2*n_bins_2), 
                                       se_ar= rep(NA, nsubj_2*n_bins_2), 
                                       t_ar=rep(NA, nsubj_2*n_bins_2), 
                                       p_ar=rep(NA, nsubj_2*n_bins_2)
                                       # Estimate_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # t_vl=rep(NA, nsubj_2*n_bins_2), 
                                       # p_vl=rep(NA, nsubj_2*n_bins_2),
                                       # Estimate_br= rep(NA, nsubj_2*n_bins_2), 
                                       # t_br= rep(NA, nsubj_2*n_bins_2), 
                                       # p_br= rep(NA, nsubj_2*n_bins_2),
                                       # Estimate_ar_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # t_ar_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # p_ar_vl= rep(NA, nsubj_2*n_bins_2),
                                       # cov= as.character(rep(NA, nsubj_2*n_bins_2)
                                                         )
timecourse_60bin_result_df_for_bp

# now fit level 1 within individual tests
0 = 1 # remember to always rezero it
s=2
b = 3
# nbins

n_bins_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$timebin_no)
subject_id_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$ssid)

s = 1
b = 2

for (s in 1:length(subject_id2)) {
  for (b in 1:length(n_bins_3)) {

    message(sprintf("$$$$$RUNING ssid %s timebin %i", subject_id2[s], n_bins_3[b]))
        lm_bin_pup  <- lm(pup_basCor ~ arousal_c,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins_NT_55,
                                    ssid ==  subject_id2[s] &
                                    timebin_no == n_bins_3[b]))
        # save the summary    
        lm_bin_pup_summary<- summary(lm_bin_pup)

        # store statistics for particiapnt and timebin
        timecourse_60bin_result_df_for_bp[i,1]<- subject_id[s] #ssid 
        timecourse_60bin_result_df_for_bp[i,2]<- n_bins_3[b] #timebin
          # timecourse_60bin_result_df[b,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            timecourse_60bin_result_df_for_bp[i,3] <- lm_bin_pup_summary$coefficients[2] #estimate, note to avoid intercept start on 2 for estimate, then 4 for se, the 6 for t and so on
            timecourse_60bin_result_df_for_bp[i,4] <- lm_bin_pup_summary$coefficients[4] #se
            timecourse_60bin_result_df_for_bp[i,5] <- lm_bin_pup_summary$coefficients[6] #t
             timecourse_60bin_result_df_for_bp[i,6] <- lm_bin_pup_summary$coefficients[8] #p

       i = i+1
     # b = b+1
  }

  }

timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp[442:nrow(timecourse_60bin_result_df_for_bp),]

# heatmap

library(viridis)
install.packages('hrbrthemes')

library(hrbrthemes)
timecourse_60bin_result_df_for_bp%>%
  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins))+
  geom_tile(aes(fill = Estimate_ar))+
  scale_fill_viridis(discrete=FALSE) 
  theme_ipsum()
  theme_classic()

  ?p.adjust
  timecourse_60bin_result_df_for_bp$p_ar_adjust<- p.adjust(timecourse_60bin_result_df_for_bp$p_ar,
                                                           method = "bonferroni", n = 55)

timecourse_60bin_result_df_for_bp<-  timecourse_60bin_result_df_for_bp%>%
    group_by(ssid)%>%
    mutate(p_adjusted = p.adjust(p_ar, method = "bonferroni", n = n()))

timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins))+
  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(x = timebins/10, y = t_ar))+
  stat_summary(geom = "line", size = 2)+
  stat_summary( geom = "errorbar", mult = 1) 
  stat_summary()

  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

  timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(x = timebins/10, y = t_ar))+
  stat_summary(geom = "line", size = 2)+
  stat_summary( geom = "errorbar", mult = 1) 
  stat_summary()

  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

  # count
  alpha
  timecourse_60bin_result_df_for_bp$p_adjusted_count<- 
    timecourse_60bin_result_df_for_bp$p_adjusted< alpha

   timecourse_60bin_result_df_for_bp$p_count<- 
    timecourse_60bin_result_df_for_bp$p_ar< alpha

  table(  timecourse_60bin_result_df_for_bp$p_adjusted_count)

  table(  timecourse_60bin_result_df_for_bp$p_count)

# flag max
  timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp%>%
    group_by(ssid)%>%
    # mutate(max_T = if_else(p_adjusted_count == TRUE, max(t_ar), NULL))
   mutate(max_T =  max(t_ar))

p.adjust(.05, method = "bonferroni", 55)

.05/55
# 0.0009

# new t = 4.5

timecourse_60bin_result_df_for_bp%>%
  group_by(ssid)%>%
  summarize_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(x = as.factor(as.numeric(ssid)), y = t_ar))+
  geom_point(size = 2, color = "blue")+
  geom_segment( aes(x=as.factor(as.numeric(ssid)), xend=as.factor(as.numeric(ssid)), 
                    y=0, yend=t_ar),color = "blue")+
  geom_hline(yintercept = 3.5, linetype = "dashed")+
  coord_flip()+
  theme_bw()
  geom_line()

  # just p value

  timecourse_60bin_result_df_for_bp%>%
  group_by(ssid)%>%
  summarize_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(x = as.factor(as.numeric(ssid)), y = p_ar))+
  geom_point(size = 2, color = "blue")+
  geom_segment( aes(x=as.factor(as.numeric(ssid)), xend=as.factor(as.numeric(ssid)), 
                    y=0, yend=p_ar),color = "blue")+
  geom_hline(yintercept = .05, linetype = "dashed")+
  coord_flip()+
  theme_bw()
  geom_line()

  # lets for a minute assume the regukar o is fine
  timecourse_60bin_result_df_for_bp%>%
    group_by(ssid)

  # alpha, the false positive rate
n <- Nsub

indsig_ts = timecourse_60bin_result_df_for_bp$p_ar <alpha
# table(indsig)

# lets start with valence
k_ar_ts <- sum(indsig_ts)
table(indsig_ts)

timecourse_60bin_result_df_for_bp%>%
  group_by(ssid)%>%
  mutate(p_count_sum_sidsum(p_count))%>%
  mutate(= k_ar_ts_sid = )

?binom.test
binom.test(k_ar_ts, 3025, 0.05, alternative="two.sided",  )

 #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            # valence

            timecourse_60bin_result_df[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            # brighteness

            timecourse_60bin_result_df[i,8]<-
            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
            timecourse_60bin_result_df[i,9]<-
              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
            timecourse_60bin_result_df[i,10]<-
              lmer_bin_pup_summary[["coefficients"]][4,5] # p value

            # interaction arousal x brighteness

            timecourse_60bin_result_df[i,11]<-
            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
            timecourse_60bin_result_df[i,12]<-
              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_60bin_result_df[i,13]<-
              lmer_bin_pup_summary[["coefficients"]][5,5] # p value

### 2022-05-25 Subj_Obj_Ar_Bayes_Prev1.Rmd
change of storage location

>>>>

limited coherence
```{r}
View(db_full6new_hr_fix_stim_nt1.1)
db_full6new_hr_fix_stim_nt1.1

# check the proximal distal problem
# maybe coherecne increases with increasing action potential
# use norm first and keep stim with high intensity

# use 4.5
db_full6new_hr_fix_stim_nt1.1 %>%
  # subset(ArousalMean>6)%>%
  subset(arousal > 2)%>%
   mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  group_by(ssid)%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid, mediansplit_ground_valence,cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid,-mediansplit_ground_valence)%>%
  group_by(ssid, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value, color = key))+
  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
  geom_jitter(width = .1, alpha = .5)+
  stat_summary(geom = 'pointrange', color = "black")+
    # facet_grid(~mediansplit_ground_valence)+
  geom_hline(yintercept = .2)

  p$graphstyle

  # ggplot(aes(ArousalMean))+
  # geom_histogram()
  # geom_density()

  # intensity thing doesnt work but what abotu bayesian prevalence

  db_full6new_hr_fix_stim_nt1.1_bp<-
db_full6new_hr_fix_stim_nt1.1 %>%
   mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%

  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])

  # store correlation and ps

  cor.test(db_full6new_hr_fix_stim_nt1.1_bp$pup_basCor, db_full6new_hr_fix_stim_nt1.1_bp$CDA.PhasicMax, use = "complete")$p.value

db_full6new_hr_fix_stim_nt1.1_bp<-  db_full6new_hr_fix_stim_nt1.1_bp%>%
  group_by(ssid)%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"),
         cor_hr_pup_pval = cor.test(Bio_Mean_HR_dif, pup_basCor, use = "complete")$p.value)%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"),
         cor_hr_scr_pval = cor.test(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete")$p.value)%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"),
         cor_pup_scr_pval = cor.test(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete")$p.value)

View(db_full6new_hr_fix_stim_nt1.1_bp)

db_full6new_hr_fix_stim_nt1.1_bp2 <- db_full6new_hr_fix_stim_nt1.1_bp %>%
  group_by(ssid, subject)%>%
  summarise_at(c("cor_hr_pup", "cor_hr_pup_pval", "cor_hr_scr","cor_hr_scr_pval",
                 "cor_pup_scr", "cor_pup_scr_pval"), mean, na.rm = TRUE)

?cor
db_full6new_hr_fix_stim_nt1.1_bp2<- db_full6new_hr_fix_stim_nt1.1_bp2 %>%
  mutate(indsig_hr_pup = cor_hr_pup_pval<alpha,
         indsig_hr_scr = cor_hr_scr_pval<alpha,
         indsig_pup_scr = cor_pup_scr_pval<alpha,
         # onetailed
         indsig_hr_pup_1t = (cor_hr_pup_pval/2)<alpha,
         indsig_hr_scr_1t = (cor_hr_scr_pval)/2<alpha,
         indsig_pup_scr_1t = (cor_pup_scr_pval)/2<alpha)

sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup)
sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr)
sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr)

sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup_1t)
sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr_1t)
sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr_1t)

# do bayesian prevalence n the regular

# two-tailed
k_hr_pup <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup)
k_hr_pup/50

t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_hr_pup, 
       alternative = c("two.sided"))
# t = 0.94557, df = 49, p-value = 0.349

binom.test(k_hr_pup, 50)
# number of successes = 6, number of trials = 50, p-value = 0.00000003244

xvals <- seq(0, 1, .01)
pdf_hr_pup <- bayesprev_posterior(xvals, k_hr_pup, 50) # function needed
pdf_hr_pup

plot(xvals, pdf_hr_pup, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_hr_pup, 50)
# 0.07368421
pmap = bayesprev_posterior(xmap, k_hr_pup, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_hr_pup, 50)
pbound = bayesprev_posterior(xbound, k_hr_pup, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_hr_pup, 50)
# 0.08783098 0.34143456
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_hr_pup, 50)
h2 = bayesprev_posterior(i2, k_hr_pup, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# hr scr - 2t

````{r}

xvals <- seq(0, 1, .01)
k_hr_scr <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr)
# k_hr_pup/50

t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_hr_scr, 
       alternative = c("two.sided"))

binom.test(k_hr_pup, 50)
binom.test(k_hr_scr, 50, p = 0)
# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022

pdf_hr_scr <- bayesprev_posterior(xvals, k_hr_scr, 50) # function needed
pdf_hr_scr

plot(xvals, pdf_hr_scr, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_hr_scr, 50)
pmap = bayesprev_posterior(xmap, k_hr_scr, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_hr_scr, 50)
pbound = bayesprev_posterior(xbound, k_hr_scr, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_hr_scr, 50)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_hr_scr, 50)
h2 = bayesprev_posterior(i2, k_hr_scr, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# scr pup 22t
# plot posterior distribution of population prevalence

xvals <- seq(0, 1, .01)
k_pup_scr <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr)
# k_pup_pup/50
binom.test(k_pup_scr, 50, p = 0.5)
# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
# number of successes = 6, number of trials = 50, p-value = 0.00000003244

pdf_pup_scr <- bayesprev_posterior(xvals, k_pup_scr, 50) # function needed
pdf_pup_scr

plot(xvals, pdf_pup_scr, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_pup_scr, 50)
pmap = bayesprev_posterior(xmap, k_pup_scr, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_pup_scr, 50)
pbound = bayesprev_posterior(xbound, k_pup_scr, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_pup_scr, 50)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_pup_scr, 50)
h2 = bayesprev_posterior(i2, k_pup_scr, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# one tailed 
# hr_pup

k_hr_pup_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup_1t)
k_hr_pup_1t/50

xvals <- seq(0, 1, .01)
pdf_hr_pup_1t <- bayesprev_posterior(xvals, k_hr_pup_1t, 50) # function needed
pdf_hr_pup_1t

plot(xvals, pdf_hr_pup_1t, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_hr_pup_1t, 50)
pmap = bayesprev_posterior(xmap, k_hr_pup_1t, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_hr_pup_1t, 50)
pbound = bayesprev_posterior(xbound, k_hr_pup_1t, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_hr_pup_1t, 50) #0.02561301 0.24410451
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_hr_pup_1t, 50)
h2 = bayesprev_posterior(i2, k_hr_pup_1t, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# hr scr_1t - 1t

xvals <- seq(0, 1, .01)
k_hr_scr_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr_1t)
# k_hr_pup/50
binom.test(k_hr_scr_1t, 50, p = 0)
# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022

pdf_hr_scr_1t <- bayesprev_posterior(xvals, k_hr_scr_1t, 50) # function needed
pdf_hr_scr_1t

plot(xvals, pdf_hr_scr_1t, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_hr_scr_1t, 50)
pmap = bayesprev_posterior(xmap, k_hr_scr_1t, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_hr_scr_1t, 50)
pbound = bayesprev_posterior(xbound, k_hr_scr_1t, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_hr_scr_1t, 50) #0.1214375 0.3875048
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_hr_scr_1t, 50)
h2 = bayesprev_posterior(i2, k_hr_scr_1t, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# scr pup 1t
# plot posterior distribution of population prevalence
?t.test
t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_pup_scr, 
       alternative = c("greater"))

xvals <- seq(0, 1, .01)
k_pup_scr_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr_1t)
# number of successes = 12, number of trials = 50, p-value = 0.0003059
# k_pup_pup/50
binom.test(k_pup_scr_1t, 50, p = 0.5)
# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
# number of successes = 6, number of trials = 50, p-value = 0.00000003244

pdf_pup_scr_1t <- bayesprev_posterior(xvals, k_pup_scr_1t, 50) # function needed
pdf_pup_scr_1t

plot(xvals, pdf_pup_scr_1t, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

xmap = bayesprev_map(k_pup_scr_1t, 50)
pmap = bayesprev_posterior(xmap, k_pup_scr_1t, 50)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_pup_scr_1t, 50)
pbound = bayesprev_posterior(xbound, k_pup_scr_1t, 50)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_pup_scr_1t, 50) #0.08783098 0.34143456
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_pup_scr_1t, 50)
h2 = bayesprev_posterior(i2, k_pup_scr_1t, 50)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
